Test if analytic derivation of geodesic distance for curves from sim_functional_data.R

### 2019-06-25 test_analytic_geodesic_distance.Rmd
added more intersting warping scenario 5 and updated compare_methods

The function sim_functional_data.R allows specification of several simulatin scenarios. The samplesize should be set very high so that Floyd's algorithm works well on the noiseless data. The number of time grid points K also should be high so that the vector data really represents the functional curve.

@@

```{r}
# Generate data
sim <- sim_functional_data(sce=4,samplesize=200,K=100,plot_true=1,reg_sampling=0)
```

The output actually contains more than just the simulated functional data. In particular, it contains the in-sample pairwise geodesic distance matrix (analytic_geo) via analytic derivation. The purpose of this notebook is to see if our analytic derivations match numerical results.

@@

We would like to compare sim$analytic_geo to geodesic distance estimation via Floyd's algorithm for the noiseless (discretised) curve. This algorithm is guaranteed to do well if we sample the manifold densely enough? (That's why we set the samplesize to be quite high initially.)

>>>>

The function sim_functional_data.R allows specification of several simulatin scenarios. 
# The samplesize should be set very high so that Floyd's algorithm works well on the noiseless data. The number of time grid points K also should be high so that the vector data really represents the functional curve.

@@

```{r}
# Generate data
sim <- sim_functional_data(sce=5,samplesize=200,K=30,plot_true=1,reg_sampling=1)
```

The output contains the in-sample pairwise geodesic distance matrix (analytic_geo) via analytic derivation. The purpose of this notebook is to see if our analytic derivations match numerical results.

@@

Specifically, we would like to compare sim$analytic_geo to geodesic distance estimation via Floyd's algorithm for the noiseless (discretised) curve. This algorithm is guaranteed to do well if we sample the manifold densely enough? Setting the samplesize very high is not enough for this, a concentrated sampling of the manifold is actually needed. More on this in sim_functiona_data.R documentation. The number of grid points should not be too low since then the L2 distance between the discretized curves won't be well estimated. K=30 seems to suffice in general.
